\begin{thebibliography}{5} 
\addcontentsline{toc}{chapter}{Bibliography} 
\bibitem{madison}Krebs On Security [2015] \emph{"Online Cheating Site AshleyMadison Hacked"}. Available on http://krebsonsecurity.com.
\bibitem{sony}James Cook [December 16, 2014] \emph{"Sony Hackers Have Over 100 Terabytes Of Documents. Only Released 200 Gigabytes So Far"} Available on http://uk.businessinsider.com/.
\bibitem{bplustree}Amittai Aviram [2010] \emph{"B+Tree Implementation"} Available on http://www.amittai.com/prose/bpt.c.
\bibitem{source}Bernagozzi Stefano [2015] \emph{"Source Code Of The Project"} Available on https://github.com/ste93/thesis\_code.
\bibitem{microsoft}Microsoft SQL server [2008] \emph{Detailed Description.}
https://technet.microsoft.com/en-us/library/cc278098(v=sql.100).aspx.
\bibitem{oracle}Oracle encrypted database \emph{Description of the database.}
https://docs.oracle.com/cd\allowbreak{}/B19306\_01/network.102/b14268/asotrans.htm\#BABJJAIG.
\bibitem{ibm}IBM DB2 encryption. https://www-01.ibm.com/support/knowledgecenter/SSEPGG\allowbreak{}\_10.5.0/com.ibm.db2.luw.admin.sec.doc/doc/c0061758.html.
\bibitem{google}Mattsson, U., Protegrity Corporation, 2005. \emph{Combined hardware and software based encryption of databases.} U.S. Patent 6,963,980.
\bibitem{efs}Encrypted File System Windows http://windows.microsoft.com/en-us/windows/what-is-encrypting-file-system\#1TC=windows-7
\bibitem{cina}Yang, Z., Zhong, S. and Wright, R.N., 2006. \emph{Privacy-preserving queries on encrypted data}. In Computer Security–ESORICS 2006 (pp. 479-495). Springer Berlin Heidelberg.
Vancouver	
\bibitem{tamper}Özsoyoglu, G., Singer, D.A. and Chung, S.S., 2003, August. \emph{Anti-Tamper Databases: Querying Encrypted Databases}. In DBSec (pp. 133-146).
\bibitem{homo1}Gentry, C., 2009. \emph{A fully homomorphic encryption scheme} (Doctoral dissertation, Stanford University).
\bibitem{homo2}Smart, N.P. and Vercauteren, F., 2010. \emph{Fully homomorphic encryption with relatively small key and ciphertext sizes}. In Public Key Cryptography–PKC 2010 (pp. 420-443). Springer Berlin Heidelberg.
\bibitem{hard}Song, D.X., Wagner, D. and Perrig, A., 2000. \emph{Practical techniques for searches on encrypted data}. In Security and Privacy, 2000. S\&P 2000. Proceedings. 2000 IEEE Symposium on (pp. 44-55). IEEE.
\bibitem{openssl}Openssl EVP encryption documentation.  https://wiki.openssl.org/index.php/EVP\allowbreak{}\_Symmetric\_Encryption\_and\_Decryption.
%\bibitem{light}Samanthula, B.K., Jiang, W. and Bertino, E., 2014. \emph{Lightweight and Secure Two-Party Range Queries over Outsourced Encrypted Databases.} arXiv preprint arXiv:1401.3768.
\end{thebibliography} 

